Localization properties, observable character and computational reliability of the linear response in open systems

### 2018-06-12 AnalyticStructure_main.tex
continuing

% The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation states using a procedure  
% analogous to the one depicted in section \ref{SEopenSystem}. So we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and express the solution of 
% \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation
It is easy to see that the solution of equation \eqref{fluctuationStateEqMotion1} can be casted in the form of
a set of scattering problems:
%a self-consistent inhomogeneous Helmholtz equation
\be\lb{rhoPrimeFluctuationStateDef2}
\ket{f_p^\Phi(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s_p^\Phi(\omega)} \;,
\ee
with:%here in this case the source term contains further addend apart from the unperturbed potential and reads:
\be
\ket{s_p^\Phi(\omega)} =  \op V\ket{f_p^\Phi(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
\ee
As a stringent hypothesis, 
let us now assume that the operator $\op Q_0(\op V'(\omega) + \op \Phi(\omega))$ is, line $\op V$ nonzero on a bounded real-space domain.
%The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
%the source term depends also from the perturbation added to the system so this analysis applies only to the class 
%of perturbing field for which $\ket{\op\Phi\psi_p}$ is localized, when projected
%in the $\r$-representation. 
It emerges that, for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that govern the localization properties of the corresponding 
fluctuation state. For $\omega > |\eps_p|$,  the Helmholtz kernel behaves as a spherical wave and  gives raise to a $f_p(\omega,\r)$ delocalized in the whole accessible space,
whereas for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.

>>>>

% The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation states using a procedure  
% analogous to the one depicted in section \ref{SEopenSystem}. So we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and express the solution of 
% \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation
It is easy to see that the solution of equation \eqref{fluctuationStateEqMotion1} can be casted in the form of
a set of scattering problems:
%a self-consistent inhomogeneous Helmholtz equation
\be\lb{rhoPrimeFluctuationStateDef2}
\ket{f_p^\Phi(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s_p^\Phi(\omega)} \;,
\ee
with:%here in this case the source term contains further addend apart from the unperturbed potential and reads:
\be
\ket{s_p^\Phi(\omega)} =  \op V\ket{f_p^\Phi(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
\ee
As a \emph{stringent} hypothesis, 
let us now assume that the operator $\op Q_0(\op V'(\omega) + \op \Phi(\omega))$ is, like $\op V$, localized, i.e. nonzero \emph{only}
on a bounded real-space domain.
%The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
%the source term depends also from the perturbation added to the system so this analysis applies only to the class 
%of perturbing field for which $\ket{\op\Phi\psi_p}$ is localized, when projected
  %in the $\r$-representation. 
It can be seen that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level 
that govern the localization properties of the corresponding 
fluctuation state. Even when the above locality argument holds true, for $\omega > |\eps_p|$, 
the Helmholtz kernel behaves as a spherical wave and  gives raise to a $f_p(\omega,\r)$ which is \emph{delocalized} in the whole accessible space.
Only for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $f_p(\omega,\r)$ \emph{may} 
exhibit a bound-state behavior in the long range, once again provided that the above locality arguments on $\op V'$ and $\Phi$ are valid.
